
\documentclass{scrartcl}

\reversemarginpar % Move the margin to the left of the page 

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage{bold-extra}
\usepackage{marvosym}
\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document

\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}} % Font color of your name at the top

\usepackage{hyperref, xcolor, color, soul} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Spring 2011} % Set the width of the date box in each block

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here

\newcommand{\IndentLine}{\hangindent=2em\hangafter=0\noindent\raggedright}

%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

\begin{cv}{\spacedallcaps{Karan Singh}}\vspace{1.5em} % Your name

\hspace{-3.0em}\noindent\spacedlowsmallcaps{Personal Information}
\vspace{1em}\\ % Personal information heading
{\IndentLine Princeton University \hfill \Letter\href{mailto:karans@princeton.edu}{karans@princeton.edu}\\ \IndentLine 35 Olden Street \hfill \Mundus\href{http://cs.princeton.edu/~karans}{cs.princeton.edu/\textasciitilde karans} \\
\IndentLine Princeton, NJ 08540 \hfill \Mobilefone +1 (609) 516 5555\\}

\vspace{1.5em} % Extra white space between the personal information section and goal

\noindent\spacedlowsmallcaps{Research Interests}\vspace{1em} % Goal heading, could be used for a quotation or short profile instead

\Description{Theoretical and applied Machine Learning, with a focus on \textbf {Reinforcement Learning} and \textbf{Dynamical Systems}. Generative Models, Online Learing, Learning with Partial Feedback, Optimization. }
%\vspace{1em} % Goal text

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Education}\vspace{1em}

\NewEntry{2015-Present}{\textsc{\color{Maroon} Princeton University}}

\Description{\MarginText{PhD Candidate in Computer Science \\ \hfill \\ Reinforcement Learning, Dynamical Systems} GPA: 4.0\ \ $\cdotp$\ \ \textit{PhD Candidate}\ \ $\cdotp$\ \ Computer Science\newline 
My research is focused on algorithms for machine learning with {\em provable guarantees} on computational and statistical efficiency, with an attentive emphasis on \textbf{interactive learning algorithms}. My prior research efforts have yielded provable methods for learning \textbf{Linear Dynamical Systems} (\textbf{Spotlight} at NIPS 2017, \textbf{Oral} at NIPS 2018) and designing controls for the same, despite the non-convex nature of the maximum likelihood problem. My recent works seek to address issues concerning exploration in Reinforcement Learning and those that arise when dealing with continuous state and action spaces.
\newline
Advisor: Prof.~Elad \textsc{Hazan}}

%------------------------------------------------

\NewEntry{2011-2015}{\textsc{\color{Maroon} Indian Institute of Technology, Kanpur}}

\Description{\MarginText{Bachelor of Technology, Computer Science \\ \hfill \\ \textbf{Ranked 1\textsuperscript{st}} (among 820 students)}GPA: 10.0\ \ $\cdotp$\ \ \textit{Bachelor of Technology}\ \ $\cdotp$\ \ Computer Science\newline
Following a rigorous introduction to computer systems and engineering, my coursework included 12 graduate-level courses on theoretical computer science, machine learning, and mathematics. My senior thesis details sketch-based algorithms for machine learning, and lower bounds in the streaming model. \\
\hfill\\
Awarded the \textbf{President's Gold Medal} for the best academic performance in the graduating class among all disciplines.
}

%------------------------------------------------

%\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Publications} \vspace{1em}\\
\Description{\MarginText{Preprint}Elad Hazan, Sham Kakade, \textbf{Karan Singh}, Abby Van Soest. Provably Efficient Maximum Entropy Exploration.}
\vspace{-0.25em}
\Description{\MarginText{Preprint}Naman Agarwal, Brian Bullins, Elad Hazan, Sham Kakade, \textbf{Karan Singh}. Online Control with Adversarial Disturbances.}
\vspace{-0.25em}
\Description{\MarginText{NIPS 2018 \textbf{Oral Presentation}}Elad Hazan, Holden Lee, \textbf{Karan Singh}, Cyril Zhang and Yi Zhang. Spectral Filtering for General Linear Dynamical Systems. In the \textit{Advances in Neural Information Processing Systems 31 (NIPS), 2018}.}
\vspace{-0.25em}
\Description{\MarginText{ICLR 2018 Workshop}Sanjeev Arora, Elad Hazan, Holden Lee, \textbf{Karan Singh}, Cyril Zhang and Yi Zhang. Towards Provable Control for Unknown Linear Dynamical Systems. \textit{International Conference on Learning Representations, Workshop Track, 2018}.}
\vspace{-0.25em}
\Description{\MarginText{Non-convex Workshop, ICML 2018.}Naman Agarwal, Brian Bullins, Xinyi Chen, Elad Hazan, \textbf{Karan Singh}, Cyril Zhang and Yi Zhang. The Case for Full-Matrix Adaptive Regularization. \textit{International Conference on Machine Learning, Non-convex Workshop, 2018}.}
\vspace{-0.25em}
\Description{\MarginText{NIPS 2017 \textbf{Spotlight}}Elad Hazan, \textbf{Karan Singh} and Cyril Zhang. Learning Linear Dynamical Systems via Spectral Filtering. In the \textit{Advances in Neural Information Processing Systems 30 (NIPS), 2017}.}
\vspace{-0.25em}
\Description{\MarginText{ICML 2017}Naman Agarwal and \textbf{Karan Singh}. The Price of Differential Privacy for Online Learning. In the \textit{Proceedings of the 34th International Conference on Machine Learning (ICML), 2017}. \href{http://proceedings.mlr.press/v70/agarwal17a.pdf}{PDF}}
\vspace{-0.25em}
\Description{\MarginText{ICML 2017}Elad Hazan, \textbf{Karan Singh} and Cyril Zhang. Efficient Regret Minimization in Non-Convex Games. In the \textit{Proceedings of the 34th International Conference on Machine Learning (ICML), 2017}. \href{http://proceedings.mlr.press/v70/hazan17a/hazan17a.pdf}{PDF}}
\vspace{-0.25em}
\Description{\MarginText{DEML Workshop, ICML 2016}Irineo Cabreros, \textbf{Karan Singh} and Angela Zhou. A Mixture Model for Crowdsourcing. A preliminary version appeared at the \textit{ICML Workshop on Data Efficient Machine Learning, 2016}.}
\vspace{-0.25em}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Experience}

\NewEntry{Summer 2018}{Intern, \textsc{\color{Maroon} Google AI, Princeton}}

\Description{\MarginText{Google AI, Princeton}Designed an efficient full-matrix adaptive regularization algorithm for optimizing deep neural networks. Using an efficient low-rank matrix inversion subroutine, the optimizer outperforms popular algorithms like ADAM in language-based tasks by harnessing higher-order correlations. Released an open-source implementation in Tensorflow \& PyTorch.\\
Host: Prof. Yoram \textsc{Singer}}

\NewEntry{Summer 2014}{Intern, \textsc{\color{Maroon} Microsoft Research, Redmond}}

\Description{\MarginText{Microsoft Research Redmond}Developed a Programming-by-Natural-Language framework to synthesize programs in targeted domain-specific languages given intents expressed as natural language prompts. The system supported multiple rounds of end-user interactions making it more robust than traditional NLP approaches. Concrete instantiations of the framework offer an interactive experience for repetitive data manipulation and summarization tasks.\\
Host: Dr. Sumit \textsc{Gulwani}}
%\vspace{1em} % Extra space between major sections

\noindent\spacedlowsmallcaps{Awards and Distinctions}\vspace{0em}
\vspace{-0.25em}

\Description{
\MarginText{\hfill \\ \hfill \\ \hfill \\ Awards for Exceptional Academic Performance  \\ \hfill \\ \hfill \\ \hfill \\ \hfill \\ \hfill \\ Science Olympiads and Scholarships}	
\begin{itemize}
\item[\Forward] \textbf{Ranked 1st} in the department (among 96 students) and the institute \textbf{(among 820 students)} at the Indian Institute of Technology, Kanpur.\\
\item[\Forward] Awarded the \textbf{President's Gold Medal} for the best academic performance in the graduating class in all disciplines.\\
\item[\Forward] Awarded the \textbf{General Proficiency Medal} for the best academic performance in the discipline of Computer Science.\\
\item[\Forward] Awarded the \textbf{Academic Excellence Award} for 3 years and the grade A* for \textbf{exceptional performance} in 14 courses.
\end{itemize}
%\hfill \\
%\begin{itemize}
%\item[\Forward] \textbf{Ranked 4th in India} in the preliminary round of Google Code Jam 2012.\\
%\item[\Forward] Ranked 8th in ACM Inter Collegiate Programming Contest Asia Region Finals 2013 finals at Kanpur site.\\
%\end{itemize}
\hfill \\
\begin{itemize}
\item[\Forward] Awarded the \textbf{Gold Medal} for being in the \textbf{top 35 (0.1\%)} students in Indian National Physics Olympiad 2011.\\
\item[\Forward] Secured \textbf{All India Rank 14} in All India Engineering Entrance Examination 2011 \textbf{among 1,050,000 students}.\\
\item[\Forward] Secured \textbf{All India Rank 140} in Indian Institute of Technology Joint Entrance Examination 2011 \textbf{among 485,000 students}.\\
\item[\Forward] Awarded KVPY Fellowship (2009), the most prestigious scholarship in the discipline of science offered by Government of India at high school level.\\
\item[\Forward] Awarded National Talent Search (NTS) Scholarship in 2007.
\end{itemize}}

%\noindent\spacedlowsmallcaps{Coursework}\vspace{1em}
%\Description{\MarginText{\hfill \\ Princeton University \\ \& IIT Kanpur}
%\hspace{-0.5em} Theoretical Machine Learning $|$ Statistical Learning and Non-parametric Estimation $|$ Fairness in Machine Learning $|$ Coding Theory and Random Graphs $|$ Advanced Algorithm Design $|$ Convex and Conic Optimization $|$ Data Streaming Algorithms $|$ Randomized Algorithms $|$ Algorithmic Game Theory $|$ Linear Programming $|$ Mathematics for Machine Learning $|$ Machine Learning for Computer Vision $|$ Linear Estimation
%}

\noindent\spacedlowsmallcaps{Teaching Experience}\vspace{0em}
\vspace{-0.25em}

\Description{\MarginText{\hfill \\ Princeton University \\ \hfill \\ IIT Kanpur}
\begin{itemize}
\item[\Forward] Teaching Assistant, Introduction to Machine Learning (COS 324).
\item[\Forward] Teaching Assistant, Artificial Intelligence and Machine Learning (COS 402).
\item[\Forward] Teaching Assistant for the Data Structures and Algorithms course as one of the few undergraduate students selected.
\end{itemize}
}


%\noindent\spacedlowsmallcaps{References}\vspace{1em} 
%
%\begin{tabular}{c c c }
%\textbf{Prof. Elad Hazan}& \textbf{Prof. Yoram Singer}& \textbf{Prof. Sham Kakade} \\
%\Letter\href{mailto:ehazan@cs.princeton.edu}{ehazan@cs.princeton.edu} & \Letter\href{mailto:y.s@cs.princeton.edu}{y.s@cs.princeton.edu} & \Letter\href{mailto:sham@cs.washington.edu}{sham@cs.washington.edu} \\
%Princeton University & Princeton University & University of Washington\\
%\end{tabular}

\end{cv}

\end{document}
