\documentclass{scrartcl}

\reversemarginpar % Move the margin to the left of the page 

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage{bold-extra}
\usepackage{marvosym}
\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document

\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}} % Font color of your name at the top

\usepackage{hyperref, xcolor, color, soul} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Spring 2011} % Set the width of the date box in each block

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here

\newcommand{\IndentLine}{\hangindent=2em\hangafter=0\noindent\raggedright}

%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

\begin{cv}{\spacedallcaps{Karan Singh}}\vspace{1.5em} % Your name

\hspace{-3.0em}\noindent\spacedlowsmallcaps{Personal Information}
\vspace{0.5em}\\ % Personal information heading
{\IndentLine Princeton University \hfill \Letter\href{mailto:karans@princeton.edu}{karans@princeton.edu}\\ \IndentLine 35 Olden Street \hfill \Mundus\href{http://cs.princeton.edu/~karans}{cs.princeton.edu/\textasciitilde karans} \\
\IndentLine Princeton, NJ 08540 \hfill \Mobilefone +1 (609) 516 5555\\}

\vspace{1em} % Extra white space between the personal information section and goal

\noindent\spacedlowsmallcaps{Research Interests}\vspace{1em} % Goal heading, could be used for a quotation or short profile instead

\Description{Theoretical and applied Machine Learning, with a focus on Interactive Systems. Reinforcement Learning, Generative Models, Online Learning.\\
Privacy and Fairness in Machine Learning.}
%\vspace{1em} % Goal text

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Education}\vspace{1em}

\NewEntry{2015-Present}{Princeton University}

\Description{\MarginText{PhD Candidate in Computer Science}GPA: 4.0\ \ $\cdotp$\ \ \textit{PhD Candidate}\ \ $\cdotp$\ \ Computer Science\newline 
My research is focussed on algorithms for machine learning with provable gurantees on computational and statistical efficiency, with an attentive emphasis on {\bf interactive learning algorithms}. Recent efforts have yielded rigorous methods for learning {\bf Linear Dynamical Systems}, and algorithms for {\bf Reinforcement Learning} with improved generalization performance.\newline
Advisor: Prof.~Elad \textsc{Hazan}}

%------------------------------------------------

\NewEntry{2011-2015}{Indian Institute of Technology, Kanpur}

\Description{\MarginText{Bachelor of Technology, Computer Science \\ \hfill \\ Ranked 1\textsuperscript{st} (among 820 students)}GPA: 10.0\ \ $\cdotp$\ \ \textit{Bachelor of Technology}\ \ $\cdotp$\ \ Computer Science\newline
Following a rigorous introduction to computer systems and engineering, my coursework included 12 graduate-level courses on theoretical computer science, machine learning, and mathematics. My senior thesis details sketch-based algorithms for machine learning, and lower bounds in the streaming model. \\
\hfill\\
Awarded the {\bf President's Gold Medal} for the best academic performance in the graduating class among all disciplines.
}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Publications ($\alpha\beta$ order)} \vspace{1em}\\
\Description{\MarginText{ICML 2017}Naman Aagrwal and {\bf Karan Singh}. The Price of Differential Privacy for Online Learning. In the \textit{Proceedings of the 34th International Conference on Machine Learning (ICML), 2017}. \href{http://proceedings.mlr.press/v70/agarwal17a.pdf}{PDF}}

\Description{\MarginText{ICML 2017}Elad Hazan and {\bf Karan Singh} and Cyril Zhang. Efficient Regret Minimization in Non-Convex Games. In the \textit{Proceedings of the 34th International Conference on Machine Learning (ICML), 2017}. \href{http://proceedings.mlr.press/v70/hazan17a/hazan17a.pdf}{PDF}}

\Description{\MarginText{arXiv}Elad Hazan and {\bf Karan Singh} and Cyril Zhang. Online Learning of Linear Dynamical Systems.}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Experience}\vspace{1em}

\NewEntry{Summer 2014}{Research Intern, \textsc{Microsoft Research, Redmond}}

\Description{\MarginText{Microsoft Research Redmond}Developed a Programming-by-Natural-Language framework to synthesize programs in targetted domain-specific languages given intents expressed as natural language prompts. The system supported multiple rounds of end-user interactions making it more robust than traditional NLP approaches. Concrete instantiations of the framework offer an interactive experience for repetitive data manipulation and summarization tasks.\\
Host: Dr. Sumit \textsc{Gulwani}}
\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Computer Skills}\vspace{1em}

\Description{\MarginText{Basic}\textsc{java}, Adobe Illustrator}

\Description{\MarginText{Intermediate}\textsc{python}, \textsc{html}, \LaTeX, OpenOffice, Linux, Microsoft Windows}

\Description{\MarginText{Advanced}Computer Hardware and Support}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	OTHER INFORMATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Other Information}\vspace{1em}

\Description{\MarginText{Awards}2011\ \ $\cdotp$\ \ School of Business Postgraduate Scholarship}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{2010\ \ $\cdotp$\ \ Top Achiever Award -- Commerce}

%------------------------------------------------

\vspace{1em}

\Description{\MarginText{Communication Skills}2010\ \ $\cdotp$\ \ Oral Presentation at the California Business Conference}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{2009\ \ $\cdotp$\ \ Poster at the Annual Business Conference in Oregon}

%------------------------------------------------

\vspace{1em}

\newlength{\langbox} % Create a new length for the length of languages to keep them equally spaced
\settowidth{\langbox}{English} % Length equals the length of "English" - if you have a longer language in your list put it here

\Description{\MarginText{Languages}\parbox{\langbox}{\textsc{English}}\ \ $\cdotp$\ \ \ Mothertongue}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\parbox{\langbox}{\textsc{Spanish}}\ \ $\cdotp$\ \ \ Intermediate (conversationally fluent)}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\parbox{\langbox}{\textsc{Dutch}}\ \ $\cdotp$\ \ \ Basic (simple words and phrases only)}

\vspace{1em} % Negative vertical space to counteract the vertical space between every \Description command

%------------------------------------------------

\Description{\MarginText{Interests}Piano\ \ $\cdotp$\ \ Cooking\ \ $\cdotp$\ \ Running\ \ $\cdotp$\ \ Chess\ \ $\cdotp$\ \ Dancing}

%----------------------------------------------------------------------------------------

\end{cv}

\end{document}